### 2021-09-14 sections/healthcare_application/main.tex
Apply proselint suggestion
Add dicussion for price of anarchy

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The two players are treated as two separate populations where each 
individual in the population is assigned a strategy. 
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each each strategy is defined as:

@@

>>>>

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The two players are treated as two separate populations where each 
individual in the population is assigned a strategy. 
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

@@

In order to analyse how efficient the strategies played at every iteration are, 
the concept of the price of anarchy is used.
Price of anarchy is a measure that is used to quantify the efficiency of a
behaviour \cite{roughgarden2005selfish}.
In other words the price of anarchy is the worst-case measure and it is
defined as:

\begin{equation}\label{eq:general_price_of_anarchy}
    \text{PoA} = \frac{\max_{s \in E} F(s)}{\min_{s \in S} F(s)}
\end{equation}

Here, \(S\) is the set of all sets of strategies \((s_1, s_2)\), \(E\) is the 
set of all possible sets of equilibria and \(F\) is the cost function to 
measure the efficiency for.
